---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# databrew: The R package of databrew

## Installation


```r
if(!require(devtools)) install.packages("devtools")
install_github('databrew/databrew')
```

## Theme

The `theme_databrew()` function, used in conjunction with `ggplot2` objects, styles a plot to the databrew brand:

```{r, eval = TRUE, echo = TRUE}
library(ggplot2)
library(databrew)
df <- data.frame(a = 1:10,
                 b = rep(1, 10),
                 c = letters[1:10])
g <- ggplot(data = df,
       aes(x = a, 
           y = b,
           color = c)) +
  geom_point(size = 15) +
  theme_databrew() +
  theme(legend.position = 'none')
g
```

## Color palettes

The `databrew` package includes a few brand-compatible color palettes. The below show their usage:

### Categorical

```{r, echo = TRUE}
n <- length(unique(df$c))
g + scale_color_manual(name = '',
                       values = make_colors(n = n))
```

### Continuous

```{r, echo = TRUE}
g + scale_color_manual(name = '',
                       values = make_colors(n = n,
                                            categorical = FALSE))
```

### Continuous (blue to green)

```{r, echo = TRUE}
g + scale_color_manual(name = '',
                       values = make_colors(n = n,
                                            categorical = FALSE,
                                            b2g = TRUE))
```

### Continuous (red to green)

```{r, echo = TRUE}
g + scale_color_manual(name = '',
                       values = make_colors(n = n,
                                            categorical = FALSE,
                                            r2g = TRUE))
```




## Details

Read the [vignette](https://htmlpreview.github.io/?https://github.com/databrew/databrew/blob/master/vignettes/vignette.html) for full details.
