---
title: "Certificate of Completion"
author: "Introduction to R"
header-includes: 
   \usepackage{fancyhdr}
output:
  pdf_document:
    fig_caption: false
params:
  name: NAME GOES HERE
classoption: landscape, a5paper
---

\pagenumbering{gobble}

\addtolength{\headheight}{1.0cm}
\pagestyle{fancyplain} 

\rhead{\begin{center}\includegraphics[height=1cm]{logo.png}\\ \href{http://databrew.cc}{www.databrew.cc}\end{center}} 

\renewcommand{\headrulewidth}{0pt} 

```{r, echo = FALSE, warning = FALSE, message = FALSE, comment = NA, error= FALSE, cache = F}

# No scientific notation
options(scipen=999)

# Packages 
library(databrew)
library(stringr)
library(cism)

# Basic knitr options
knitr::opts_chunk$set(comment = NA, 
               echo = FALSE, 
               eval = TRUE,
               warning = FALSE, 
               message = FALSE, 
               error = TRUE, 
               cache = FALSE)
```

\begin{center}
\begin{Large}

This certificates acknowledges that 

\vspace{2mm}

\end{Large}

\begin{Huge}

```{r, results = 'asis'}
cat(toupper(params$name))
```

\end{Huge}


\vspace{2mm}

\begin{Large}

Successfully completed all of the requirements of the "Introduction to R" course at the Manhiça Health Research Centre (Centro de Investigação em Saude de Manhiça) from March to May, 2017. 

\end{Large}

\vfill

\end{center}


\begin{large}
This course consisted of 12 hours of in-person instruction, in addition to approximately 24 hours of assignments. Having completed this course, the aforementioned individual has a clear grasp of the fundamentals of data reading, processing, cleaning, and visualization in R, using an assortment of packages and techniques. For validation or questions, please contact \href{mailto:info@databrew.cc}{info@databrew.cc}.
\end{large}

\begin{flushright}
\begin{small}
Unique certificate identification number: `r paste0(paste0(sample(letters, 4), collapse = '.'), sample(865732:213041902, 1), sample(letters, 1), collapse = '')`.
\end{small}
\end{flushright}
